P.berghei pir analysis

### 2021-08-31 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_Github_Pberghei_pir.Rmd
Save TPM (all samples) file

write.csv()

@@

hclusts = function(tpm){
  if(ncol(tpm$tpm) > 3){
    dists = dist(t(tpm$tpm[,-1]))
    par(cex=0.7)
    plot(hclust(dists),
         main = tpm$experiment)
  }
}

lapply(expt_tpms, hclusts)
```

>>>>

write.csv(berghei_tpm,
          'berghei_tpm_oldNamesAllSamples.csv')

@@

lapply(expt_tpms, function(tpm){
  if(ncol(tpm$tpm) > 3){
    dists = dist(t(tpm$tpm[,-1]))
    par(cex=0.7)
    plot(hclust(dists),
         main = tpm$experiment)
  }
})
```
